Efficient Coalition Formation for Web Services

### 2013-03-06 papers/coalition/coalition.tex
Changes

\author{\IEEEauthorblockN{Ehsan Khosrowshahi Asl, Jamal Bentahar}
\IEEEauthorblockA{Faculty of Engineeing and Computer Science\\
Concordia University\\
Montreal, Canada\\
e\_khosr@encs.concordia.ca,bentahar@ciise.concordia.ca}
\and
\IEEEauthorblockN{Hadi Otrok, Rabeb Mizouni}
\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
Khalifa University\\
Dubai, UAE\\
hadi.otrak, rabeb.mizouni@kustar:ac:ae}
}

@@

One of the properties of CS algorithms in our scenario is tha they partition web services with low throughput rate usually join coalitions with less request rate. Since the characteristic function $v(C)$ and  the fair payoff vector of shapley value is proportional to their contribution, the web services with small contribution will get payed much less in communities having web services with throughput. On the other hand, accoring to valuation function $v(C)$ web services with high throughput will not contribute well to commuinities with low ammount of user requests. The strong web services are much more likely to deviate that coalition joining a stronger coalition, making the initial coalition unstable. 
In coalition structure formation study, as mentioned in section \ref{sec:coalition}, maximizing social welfare is more on focus. Most algorithms in this area try to maximise overall social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} ignore the stability of coalitions from individual agent point of view. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. There are even anytime algorithms designed for this end\cite{eps267179}. It can be interrupted before it would have normally terminated and yet privade a solution within a bound from the optimal one which makes it very practical to use real world applications. The problem is that they try to maximize social benefit while contradicts with interests of selfish self-interest web services. However, expirements show web services still reasonably close to optimal payoffs and tasks while we try to optimize the overall social welfare. In expirements section, we analyze these scenarios with real world web service data.

>>>>

\author{\IEEEauthorblockN{Ehsan Khosrowshahi Asl, Jamal Bentahar}
\IEEEauthorblockA{Faculty of Engineeing and Computer Science\\
Concordia University\\
Montreal, Canada\\
e\_khosr@encs.concordia.ca, bentahar@ciise.concordia.ca}
\and
\IEEEauthorblockN{Hadi Otrok, Rabeb Mizouni}
\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
Khalifa University\\
Dubai, UAE\\
hadi.otrak, rabeb.mizouni@kustar:ac:ae}
}

@@

The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has two or more master web services as members.

One of the properties of CS algorithms in our scenario is tha they partition web services with low throughput rate usually join coalitions with less request rate. Since the characteristic function $v(C)$ and  the fair payoff vector of shapley value is proportional to web services' contribution, the web services with small contribution will get paid much less in communities having web services with high throughput. On the other hand, according to valuation function $v(C)$ web services with high throughput will not contribute well to communities with low amount of user requests. The strong web services are much more likely to deviate weak coalitions, joining a stronger coalition, making the initial coalition unstable.

In coalition-formation games, formation of the coalitions is the most important aspect of in the game. These solutions focus on maximizing social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. There are $centralized$ algorithms for this end, however these approaches are generally NP-complete. The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions. 
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centrilized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. 
In our application, we prefer not having a centralized decision maker dictating all web services their decisions. Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker. The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}. The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well. It keeps splitting and mergin coalitions where it is preferred by all players inside those coalitions.
